ext_risk_copula

### 2019-02-20 ext_risk_copula.Rmd
several changes

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))

@@

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()
```

@@

qrng<-runif(10000,min=0,max=r_bf_hussell)
qr<-quantile(qrng,probs=c(.025,.975))

@@

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,4),mar=c(5.2,4.2,1.2,6.2))

@@

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()
```

@@

```{r fig_abrewer, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", rlist[i]))
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))

>>>>

```{r fig_ricker, echo=F, results="hide",cache=T, cache.extra=list(seed,res_ricker_local,res_ricker_global)}
pdf(paste(resloc,"ricker_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
#op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,6.2))
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))

@@

pdf(paste(resloc,"ricker_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

qrng<-runif(10000,min=0,max=r_bf_hassell)
qr<-quantile(qrng,probs=c(.025,.975))

@@

```{r fig_hassell, echo=F, results="hide",cache=T, cache.extra=list(seed,res_hassell_local,res_hassell_global)}
pdf(paste(resloc,"hassell_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"hassell_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_msmith, echo=F, results="hide",cache=T, cache.extra=list(seed,res_msmith_local,res_msmith_global)}
pdf(paste(resloc,"msmith_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"msmith_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_pennycuick, echo=F, results="hide",cache=T, cache.extra=list(seed,res_pennycuick_local,res_pennycuick_global)}
pdf(paste(resloc,"pennycuick_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"pennycuick_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

```{r fig_verhulst, echo=F, results="hide",cache=T, cache.extra=list(seed,res_verhulst_local,res_verhulst_global)}
pdf(paste(resloc,"verhulst_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"verhulst_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("topleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

```{r fig_abrewer, echo=F, results="hide",cache=T, cache.extra=list(seed,res_abrewer_local,res_abrewer_global)}
pdf(paste(resloc,"abrewer_ext_risk_local_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))

@@

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

pdf(paste(resloc,"abrewer_ext_risk_global_disp.pdf",sep=""),height=9,width=9)
op<-par(mfrow=c(3,3),mar=c(5.2,4.2,1.2,1.5))
